### 2024-06-25 analysis/analysis.qmd
New analysis pilot

- [ ] Issue 1: We need unique identifiers for each input component (combine: `study` + `model` + `feature` + `data` + `experiment` that would have be unique id)
- [ ] Issue 2: We `stimulus_N`
- [ ] Issue 3: measure vs statistic?
- [ ] Issue 4: We need to classify the modelling techniques into fewer number of techniques
- [ ] Issue 5: We could polish citekey into ref (xu2021us to Xu 2021 et al., ) for nicer plotting output (can be done with `str_replace`)

@@

# select regression studies with r2
tmp <- dplyr::filter(metaMER_results,dimension=="valence" & measure=="r2")
#sqrt(tmp$values) # convert from R^2 to r
tmp$stimulus_n <- 100 # ad-hoc for now

@@

```{r}

meta <- metagen(values, sqrt(values), # Fix the TE.se 
                data = tmp, 
                studlab = tmp$citekey, 
                comb.fixed = FALSE, 
                method.tau = "PM")

subgroup.analysis.mixed.effects(x = meta, 
                                subgroups = tmp$model_id)
```

>>>>

- [x] Issue 1: We need unique identifiers for each input component (combine: `study` + `model` + `feature` + `data` + `experiment` that would have be unique id)
- [x] Issue 2: We `stimulus_N`
- [x] Issue 3: measure vs statistic?
- [x] Issue 4: We need to classify the modelling techniques into fewer number of techniques (example given, but no principles defined)
- [ ] Issue 5: We could polish citekey into ref (xu2021us to Xu 2021 et al., ) for nicer plotting output (can be done with `str_replace`)

- [ ] If the _number of stimuli_ varies, divide either to separate experiments or use the largest value (see below for ad-hoc solution).

@@

# select regression studies with r2
tmp <- dplyr::filter(metaMER_results,dimension=="valence" & measure=="r2")

# Temporary clarification of N
tmp$stimulus_n[tmp$stimulus_n==" emoMusic: 1000, soundtracks: 360, chinese: 500 "]<-1000
tmp$stimulus_n[tmp$stimulus_n==" 2372 (subset of PSIC3839, total n: 3839)    "]<-2372
tmp$stimulus_n[tmp$stimulus_n==" study 1: 20; study 2: 40) % three outliers  "]<-40
tmp$stimulus_n <- as.numeric(tmp$stimulus_n)

#sqrt(tmp$values) # convert from R^2 to r
#tmp$stimulus_n <- 100 # ad-hoc for now

@@

```{r}
#| eval: true

# divide models into random forests, SVM and MLR
tmp$model_class_id <- 'MLR/PLS'
tmp$model_class_id[str_detect(tmp$model_id,'RFR|extremely randomized tree regression')]<-'RF'
tmp$model_class_id[str_detect(tmp$model_id,'svm|SVR')]<-'SVM'
table(tmp$model_class_id)
meta <- metagen(values, sqrt(values), # Fix the TE.se 
                data = tmp, 
                studlab = tmp$citekey, 
                comb.fixed = FALSE, 
                method.tau = "PM")

subgroup.analysis.mixed.effects(x = meta, 
                                subgroups = tmp$model_class_id)
```
